Multiparty Linear Regression via SPDZ

### 2017-08-01 paper/main.tex
new charts
Add files via upload

\begin{figure}[h]
  \includegraphics[width=\linewidth]{sqrt.jpg}
  \caption{ (Top) 64 bit (Bottom) 32 bit results }
  \label{fig:result1}
\end{figure}

@@

For CGD, we decide to test if L2 norm vs Linfinity would make a difference. One utilizes comparisons and the other addition and square root. 
\begin{figure}[h]
  \includegraphics[width=\linewidth]{l2.jpg}
  \caption{ (Top) 64 bit (Bottom) 32 bit results }
  \label{fig:result1}
\end{figure}

@@

N = 100000
\begin{figure}[h]
  \includegraphics[width=\linewidth]{results1.jpg}
  \caption{(Left) Comparison between different methods of solving linear systems: running time in seconds for Cholesky, LDLT, and CGD (with 5, 10, 15, and 20 iterations) as a function of input dimension. (Middle) Accuracy of CGD as a function of the input on the condition number of the input matrix $A$ with $d = 20$. (Right) Accuracy of Cholesky, LDLT, and CGD, as a function of the input dimensionality $d$. (Top) Fixed-point numbers with the $b = 80$ bits, with 60 in the fractional part. (Bottom) $b = 41$, with 28 in the fractional part}
  \label{fig:result2}
\end{figure}

N = 1000
\begin{figure}[h]
  \includegraphics[width=\linewidth]{results2.jpg}
  \caption{(Left) Comparison between different methods of solving linear systems: running time in seconds for Cholesky, LDLT, and CGD (with 5, 10, 15, and 20 iterations) as a function of input dimension. (Middle) Accuracy of CGD as a function of the input on the condition number of the input matrix $A$ with $d = 20$. (Right) Accuracy of Cholesky, LDLT, and CGD, as a function of the input dimensionality $d$. (Top) Fixed-point numbers with the $b = 80$ bits, with 60 in the fractional part. (Bottom) $b = 41$, with 28 in the fractional part}
  \label{fig:result2}
\end{figure}

\vc{talk about outliers in these cases, skews results}

@@

>>>>

\begin{figure}[h]
  \includegraphics[width=\linewidth]{sqrt.jpg}
  \caption{ (Top) 64 bit (Bottom) 32 bit results for comparing square roots}
  \label{fig:result1}
\end{figure}

@@

For CGD, we decide to test if L2 norm vs Linfinity would make a difference. One utilizes comparisons and the other addition and square root. 
\begin{figure}[h]
  \includegraphics[width=\linewidth]{l2.jpg}
  \caption{ (Top) 64 bit (Bottom) 32 bit results for L2 Norm. }
  \label{fig:result1}
\end{figure}

@@

N = 100000
\begin{figure}[h]
  \includegraphics[width=\linewidth]{results1.jpg}
  \caption{(Left) For N = 10000: Comparison between different methods of solving linear systems: running time in seconds for Cholesky, LDLT, and CGD (with 5, 10, 15, and 20 iterations) as a function of input dimension. (Middle) Accuracy of CGD as a function of the input on the condition number of the input matrix $A$ with $d = 20$. (Right) Accuracy of Cholesky, LDLT, and CGD, as a function of the input dimensionality $d$. (Top) Fixed-point numbers with the $b = 80$ bits, with 60 in the fractional part. (Bottom) $b = 41$, with 28 in the fractional part}
  \label{fig:result2}
\end{figure}

N = 1000
\begin{figure}[h]
  \includegraphics[width=\linewidth]{results2.jpg}
  \caption{(Left) For N = 1000: Comparison between different methods of solving linear systems: running time in seconds for Cholesky, LDLT, and CGD (with 5, 10, 15, and 20 iterations) as a function of input dimension. (Middle) Accuracy of CGD as a function of the input on the condition number of the input matrix $A$ with $d = 20$. (Right) Accuracy of Cholesky, LDLT, and CGD, as a function of the input dimensionality $d$. (Top) Fixed-point numbers with the $b = 80$ bits, with 60 in the fractional part. (Bottom) $b = 41$, with 28 in the fractional part}
  \label{fig:result2}
\end{figure}

\vc{need to replace with correct plot, found where the error came from}

@@

3 party results on one machine

\begin{figure}[h]
  \includegraphics[width=\linewidth]{3players.jpg}
  \caption{Results for 3 players. Since this is not the average of 30 runs, the lines aren't as straight yet. In general the results are pretty comparable to the 2 players. There is a noticeable overhead that each additional party incurs compared to running the same computation with less parties. I will include a table later to estimate the increase for each party.}
  \label{fig:result4}
\end{figure}

4 party results on one machine

\begin{figure}[h]
  \includegraphics[width=\linewidth]{4players.jpg}
  \caption{(Results for 4 players. Since this is not the average of 30 runs, the lines aren't as straight yet. In general the results are pretty comparable to the 2 players. }
  \label{fig:result4}
\end{figure}
